\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-12-09 draft.tex
compile draft for dell laptop
add game-tree.tex from sop-rie and begin mods for this project
take out game-tree for now, switch to office location of bib
compile with game tree, remove pdftex option on graphicx package (fully functional on dell)
fix rest of game-tree labels; will examine notation later
update bibtex file with info on my paper revisions

%dell laptop
%\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}

%wallis computer
\addbibresource{C:/Users/wallis/Dropbox/Research/xBibs/tradeagreements.bib}

%campus computer
%\addbibresource{C:/Apps-SU/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

\usepackage{csquotes}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true,hyperfootnotes=false]{hyperref}
\usepackage[pdftex]{graphicx}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}
\usepackage[hang,flushmargin]{footmisc} 
\usepackage[usenames,dvipsnames]{color}
%\usepackage{cite}
\usepackage{times, verbatim,bm,pifont,pdfsync}
%\usepackage[hang,flushmargin]{footmisc}%unindents footnotes

@@

>>>>

%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}

%campus computer
\addbibresource{C:/Apps-SU/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

\usepackage{csquotes}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
\usepackage[usenames,dvipsnames]{color}
\usepackage{tikz}
\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true,hyperfootnotes=false]{hyperref}
\usepackage{graphicx}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}
\usepackage[hang,flushmargin]{footmisc}

%\usepackage{cite}
\usepackage{times, verbatim,bm,pifont,pdfsync}
%\usepackage[hang,flushmargin]{footmisc}%unindents footnotes

@@

\begin{figure}
	\begin{center}
		\input{game-tree.tex}
	\end{center}
	\caption{Extensive Form\label{fig:ext}}
\end{figure}

### 2016-12-09 to-do.tex
update bibtex file with info on my paper revisions

\section{Misc.}
\begin{itemize}
	\item Define $\ga$ before using it
	\item If add back in assumption 1, add Ethier footnote
	\item standardize $\ga(e,s)$, $\ga(e)$, $\ga(s)$ throughout the text
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover [add to conclusion, it's in slides]
	\item Ben: I'm wondering how you view the time-frame over which your model is set.  On one hand a specific-factors set-up is normally associated with the short-run.  But on the other hand you have an infinite time horizon which suggests very long run.
	\item Clarify information structure
\end{itemize}

@@

\vskip.5in
Current structure of paper (August 25, 2016)
\begin{enumerate}
	\item Introduction
	\item Model
	\item Rigid Tariffs with Endogenous Political Pressure
		\begin{itemize}
			\item[3.1] Perfect External Enforcement. Proposition 1: weak bindings and ext. enforcement imply applied tariff = binding and may use binding to encourage or restrain lobbying
			\item[3.2] $\cdot$
				\begin{itemize}
					\item[3.2.1] $\cdot$
					\item[3.2.2] Prop 2: No ext enforcement: self enforcing implies $\tau^a \leq$ optimal binding with external enforcement
				\end{itemize}
		\end{itemize}
	\item Endogenous Political Pressure and the Escape Clause
		\begin{itemize}
			\item[4.1] Strong bindings: no cost when $\ga(e)$ only
			\item[4.2] Side payments: spirit not upheld, but IC
			\item[4.3] $\ga(s,e)$, Prop 3: lower binding never used
			\item[4.4] EC for endogenous politics
		\end{itemize}
	\item Conclusion
\end{enumerate}

>>>>

\section{Misc.}
\begin{itemize}
	\item Define $\ga$ before using it
	\item If add back in assumption 1, add Ethier footnote
	\item standardize $\ga(e,s)$, $\ga(e)$, $\ga(s)$ throughout the text
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dynamic choice of protection over time, gov't turnover [add to conclusion, it's in slides]
	\item Ben: I'm wondering how you view the time-frame over which your model is set.  On one hand a specific-factors set-up is normally associated with the short-run.  But on the other hand you have an infinite time horizon which suggests very long run.
	\item Clarify information structure
\end{itemize}

@@

\newpage
Current structure of paper (August 25, 2016)
\begin{enumerate}
	\item Introduction
	\item Model
	\item Rigid Tariffs with Endogenous Political Pressure
		\begin{itemize}
			\item[3.1] Perfect External Enforcement. Proposition 1: weak bindings and ext. enforcement imply applied tariff = binding and may use binding to encourage or restrain lobbying
			\item[3.2] Self-Enforcing Trade Agreements
				\begin{itemize}
					\item[3.2.1] Repeated Game
					\item[3.2.2] Prop 2: No ext enforcement: self enforcing implies $\tau^a \leq$ optimal binding with external enforcement
				\end{itemize}
		\end{itemize}
	\item Endogenous Political Pressure and the Escape Clause
		\begin{itemize}
			\item[4.1] Strong bindings: no cost when $\ga(e)$ only
			\item[4.2] Side payments: spirit not upheld, but IC
			\item[4.3] $\ga(s,e)$, Prop 3: lower binding never used
			\item[4.4] EC for endogenous politics
		\end{itemize}
	\item Conclusion
\end{enumerate}
